\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-11-28 paper.tex
update

\section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. {\news \zyang{is this right?}We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space. For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = [\vq_1,\dots,\vq_{n_p}]\in \real{m (n_p\times T)}$. }
\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis).} Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}

@@

\subsection{Preliminaries}
\subsubsection{Differentials}
\zyang{Dim of function f use the same as before}We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
\begin{equation}\label{equ:dt_to_dx}
  \left.\dert f\bigl(x(t)\bigr)\right|_{t=0}=\partial_x f\bigl(x(0)\bigr) \dot{x}(0)
\end{equation}
where $t\mapsto x(t)\in\real{n}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$. For brevity we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$. 
%The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.

@@

\new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory. Subsequently, we introduce various reachability constraints involving an ellipsoid and other geometric entities, such as points, lines, line segments, and polygons. These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning presented in \cref{chapter:ADMM review}.
}
% In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form. Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections. Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
%The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
{\news
\begin{definition}\label{sec:ellipsoidal definition}
Let robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory that contains $q'$ while satisfies the dynamic constraints.
	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}. 
\end{definition}
When considering only the velocity constraint, the \emph{reachability} set for $q'$ can be simplified as $\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\begin{remark}
  The set $\mathcal{E}$ represents a region bounded by the sum of distances from $q'$ to two fixed points $q_1$ and $q_2$. Geometrically, this describes an ellipsoid-like shape where the sum of distances from any point on the boundary $q'\in \{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)=v_{max}(t_2-t_1)\}$ to $q_1,q_2$ is constant.\zyang{is this redundant?}
\end{remark}
To make this connection explicit, we defined the \emph{reachability ellipsoid $\cE$} as:}
\begin{definition}\label{def:Reachability}
	The reachability ellipsoid $\cE$ is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
\end{definition}
\zyanghl{is this part still needed?}{The region $\cE(q_1,q_2)$ is an ellipsoid with foci at $q_1,q_2$, center $o_{\cE} = \frac{1}{2}(q_1+q_2)$, and the major radius equal to $a$. We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.}

 \begin{figure}
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}}

@@

{\news For a robot be observed at $p_1$, $t_1$, if the reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region, any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot unable to be observed at $p_2$, $t_2$. Notice that the intersection with obstacles are not considered here.} Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \cref{def:secured-plan} can be written as,
\begin{remark}\label{rmk:revised-security}
  A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{remark}

\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
{\news To simplify the problem, we apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center and the first axis of $\cF_\cE$ aligns with the foci \Cref{fig:EllipseConstraintExample}. For all reachability ellipsoid constraints, we solve the problem in $\cF_\cE$ and transform the solutions back to $\cF$ using \eqref{eq:transformations}. The transformation and its inverse is parametrized by a rotation $R^\cF_\cE$ (denoted $R$) and a translation $o^\cF_\cE$ (denoted $o$) as:
\begin{equation}\label{eq:transformations}
  \Fframe{q}=R\Eframe{q}+o,\quad
  \Eframe{q}=R\transpose(\Fframe{q}-o).
\end{equation}
where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is formed using \emph{Householder rotation} $H$ (a differentiable linear transformation used to represent rotation between two vectors, more details in \cref{sec:householder}), and $o =\frac{1}{2}(q_1+q_2)$. $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$ represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. More details of this transformation is introduced in \cref{apx:transformation}.
  % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  % \begin{align}
  %   \nu_\cF &= \frac{q_2-q_1}{\norm{q_2-q_1}}, & \nu_\cE&=[1,0,0]^T;
  % \end{align}
  % \new{see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_{\cF}$ is a function of $q_1,q_2$ while $\nu_\cE$ is constant. From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation} (see \cref{sec:householder}), while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:}
  % \begin{align} 
  %   R&=H(\nu_\cF(q_1,q_2),\nu_\cE), &o&=\frac{1}{2}(q_1+q_2).
  % \end{align}

@@

\section{Cross-trajectory co-observation planning}\label{sec:cross-trajectory}
To address the feasibility and performance trade-offs, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams. These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
\subsection{Problem overview}
We start with an unsecured MRS trajectory with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ (the ADMM-based planner in \cref{sec:ADMM-planning} without security constraints is used, but other planners are applicable). Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$. Introducing redundant robots into the MRS, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory. To ensure the fulfillment of essential tasks, at least one robot is assigned to adhere to the reference trajectory. The remaining redundant $n_p-n$ robots are strategically utilized to enhance security. These robots focus on co-observations either within their respective sub-teams, or when necessary, deviate and join another sub-team to provide necessary co-observations. The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation} that the resulting MRS plan meet the security in \cref{rmk:revised-security} while minimizing the number of additional robots required.

{\news \zyang{this version right?} To avoid confusion, \zyanghl{Can i do this? since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} We introduce \emph{checkpoint}s to devide the trajectory into observed and un-observed sections. 
\begin{definition}
The $i$th checkpoint $v_{pi}=(q_{pi},t_{i})$ for sub-team $p$ is defined by waypoint $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ where robot is observed one (or both) of its adjacent waypoints $q_{p}(t_i-1)$ and $q_{p}(t_i+1)$.
\end{definition}
For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$. To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
}
We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ are checkpoints and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist. Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph. This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.

@@

\subsection{Checkpoint graph construction}

@@

\subsubsection{Checkpoints}\label{sec:security-checkpoint}
{\news To ensure the security of the un-observed part of the trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:}
\begin{remark}
A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
\end{remark}

>>>>

\section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. {\news \zyang{is this right?}We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space. For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation. }
\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis).} Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}

@@

\subsection{Preliminaries}
\subsubsection{Differentials}
We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
\begin{equation}\label{equ:dt_to_dx}
  \left.\dert f\bigl(x(t)\bigr)\right|_{t=0}=\partial_x f\bigl(x(0)\bigr) \dot{x}(0)
\end{equation}
where $t\mapsto x(t)\in\real{n}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$. For brevity we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$. 
%The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.

@@

\new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory. We then use the ellipsoids to introduce various reachability constraints with respect to other geometric entities, such as points, lines, line segments, and polygons. These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning presented in \cref{chapter:ADMM review}.
}
% In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form. Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections. Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
%The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
{\news
\begin{definition}\label{sec:ellipsoidal definition}
Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}. 
\end{definition}

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less then $2a$, where a is the major radius of the ellipsoid. \rtronhl{It seems we do not use $c_\cE$ in the main text, move to the appendix where it is used}{We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.}}

 %Geometrically, this describes an ellipsoid shape where the sum of distances from any point on the boundary $q'\in \{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)=v_{max}(t_2-t_1)\}$ to $q_1,q_2$ is constant.\zyang{is this redundant?}
 \begin{figure}
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}}

@@

{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot  to miss a potentia observation at $p_2$, $t_2$.} \Cref{def:secured-plan} can then be restated as follows
\begin{definition}\label{rmk:revised-security}
  A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{definition}

\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
\newcommand{\oFE}{o}
{\news To use the definition of reachability ellipsoid from the section above in a computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration). %For all reachability ellipsoid constraints, we solve the problem in $\cF_\cE$ and transform the solutions back to $\cF$ using \eqref{eq:transformations}. 
From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
\begin{equation}\label{eq:transformations}
  q=R\Eframe{q}+\oFE,\quad
  \Eframe{q}=R\transpose(q-\oFE).
\end{equation}
where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see \cref{sec:householder} for details), and $o =\frac{1}{2}(q_1+q_2)$.  To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. More details on \eqref{eq:transformations} are given in \cref{apx:transformation}.
  % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  % \begin{align}
  %   \nu_\cF &= \frac{q_2-q_1}{\norm{q_2-q_1}}, & \nu_\cE&=[1,0,0]^T;
  % \end{align}
  % \new{see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_{\cF}$ is a function of $q_1,q_2$ while $\nu_\cE$ is constant. From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation} (see \cref{sec:householder}), while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:}
  % \begin{align} 
  %   R&=H(\nu_\cF(q_1,q_2),\nu_\cE), &o&=\frac{1}{2}(q_1+q_2).
  % \end{align}

@@

\section{Cross-trajectory co-observation planning}\label{sec:cross-trajectory}
To address the feasibility and performance trade-offs, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams. These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
\subsection{Problem overview}
We start with an unsecured MRS trajectory with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ (the ADMM-based planner in \cref{sec:ADMM-planning} without security constraints is used, but other planners are applicable). Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $p$-th sub-team at time $t\in\{0, \dots, T\}$. Introducing redundant robots into the MRS, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory. To ensure the fulfillment of essential tasks, at least one robot is assigned to adhere to the reference trajectory. The remaining redundant $n_p-n$ robots are strategically utilized to enhance security. These robots focus on co-observations either within their respective sub-teams, or when necessary, deviate and join another sub-team to provide necessary co-observations. The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation} that the resulting MRS plan meet the security in \cref{rmk:revised-security} while minimizing the number of additional robots required.

{\news %\zyang{this version right?} To avoid confusion, \zyanghl{Can i do this? since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} 
Our strategy is based on the following concept:
\begin{definition}
The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ at which a robot is co-observed by its teammates, and where it can leave or join a new team.
\end{definition}
For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. %, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding location and time for checkpoint $v_{pi}$.
To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
}
We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ are checkpoints and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist. Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph. This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.

@@

\subsection{Checkpoint graph construction}\label{sec:security-checkpoint}

@@

{\news To ensure the security of the un-observed part of the trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:}
\begin{remark}
A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
\end{remark}
